---
title: "Statistical Results from Modified Policy Shaping Experiments"
author: "Ishita Sarraf"
date: "2024-07-10"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading libraries and reading files

```{r}
library(dplyr)
library(ggplot2)
```

```{r}
d1 <- read.csv("AMPS_results.csv")
d2 <- read.csv("Best_Actions_Results.csv")
d3 <- read.csv("Similarity_Results.csv")
d <- read.csv("experiment_results.csv")
```

## Cleaning Data

```{r}
new1 <- d1 %>%
  group_by(Episode) %>%
  summarize(reward_per_episode = mean(Reward))
```

```{r}
new2 <- d2 %>%
  group_by(Episode) %>%
  summarize(reward_per_episode = mean(Reward))
```

```{r}
new3 <- d3 %>%
  group_by(Episode) %>%
  summarize(reward_per_episode = mean(Reward))
```

```{r}
avg_reward1 <- d1 %>%
  group_by(Episode) %>%
  summarise(sd_reward = sd(Reward),
            m = mean(Reward))
avg_reward2 <- d2 %>%
  group_by(Episode) %>%
  summarise(sd_reward = sd(Reward),
            m = mean(Reward))
avg_reward3 <- d3 %>%
  group_by(Episode) %>%
  summarise(sd_reward = sd(Reward),
            m = mean(Reward))
new_d1 <- d %>%
  filter(Experiment_Name == "AMPS") %>%
  mutate(sd_val =  avg_reward1$sd_reward,
         mean_val = avg_reward1$m) 
new_d2 <- d %>%
  filter(Experiment_Name == "Best_Action") %>%
  mutate(sd_val =  avg_reward2$sd_reward,
         mean_val = avg_reward2$m) 
new_d3 <- d %>%
  filter(Experiment_Name == "Similarity") %>%
  mutate(sd_val =  avg_reward3$sd_reward,
         mean_val = avg_reward3$m) 
combined_df <- rbind(new_d1, new_d2, new_d3)

```

## Calculate mean and sd for each curve
```{r}
d %>%
  group_by(Experiment_Name) %>%
  summarize(m = mean(Reward),
            sd = sd(Reward))
```

## Creating Comparison Graph

```{r}
ggplot(combined_df, aes(x = Episode, y = Reward, color = Experiment_Name)) +
  geom_rect(aes(xmin = 1, xmax = 5, ymin = -Inf, ymax = Inf), fill = "grey", color = NA, alpha = 0.01) +
  geom_rect(aes(xmin = 20, xmax = 25, ymin = -Inf, ymax = Inf), fill = "grey", color = NA, alpha = 0.01) +
  geom_line() +
  geom_ribbon(aes(ymin = mean_val - sd_val, ymax = mean_val + sd_val, fill = Experiment_Name), alpha = 0.2, color = NA) +
  scale_color_viridis_d() +
  scale_fill_viridis_d() +
  labs(x = "Episode Number", y = "Reward",
       title = "Reward for 50 episodes averaged over 15 runs") +
  theme_linedraw() +
  guides(color = guide_legend(title = NULL),
         fill = guide_legend(title = NULL)) +
  theme(text = element_text(size = 20),
        axis.text.x = element_text(hjust = 1),
         axis.text.y = element_text(angle = 90, vjust = 1))
```


```{r}
# Calculate mean and standard deviation for each episode and experiment
d_summary <- d %>%
  group_by(Episode, Experiment_Name) %>%
  summarise(
    mean_Reward = mean(Reward),
    sd_Reward = sd(Reward, na.rm = TRUE)
  ) %>%
  ungroup()

# Plot
ggplot(d_summary, aes(x = Episode, y = mean_Reward, color = Experiment_Name, fill = Experiment_Name)) +
  geom_line() +
  geom_ribbon(aes(ymin = mean_Reward - sd_Reward, ymax = mean_Reward + sd_Reward), alpha = 0.2) +
  labs(x = "Episode", y = "Reward", title = "Reward with Standard Deviation by Experiment") +
  theme_minimal()
```



## ANOVA and Tukey HSD

```{r}
anova_model <- aov(Reward ~ Experiment_Name, data = d)
anova_model
```
```{r}
hsd <- TukeyHSD(anova_model)
hsd
```
## Analysis

"Best_Action" and "AMPS" have significantly different mean rewards.
"Similarity" and "AMPS" have significantly different mean rewards.
There is no significant difference in mean reward between "Similarity" and "Best_Action".
We are 95% confident that the differences in mean rewards are accurate and not due to random chance assuming all assumptions for ANOVA are satisfied.

```{r}
plot(anova_model)
```

The data does not seem completely normal, and but the variance assumption seems satisfied. 